Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2021-10-24 article.rnw
Sentence-case the title, as the journal style requires.
Change to using the citation and bibliography for the "Ecology" journal.
As required by the assignment.
Add more details on the equivalently grouped models to the results.

%Referencing
\import{reference-styles/}{authoryear.tex}
\addbibresource{bibliography/references.bib}
\addbibresource{references.bib}
\usepackage{placeins} %Provides \FloatBarrier

@@

%Title Page
\title{Regularising Lotka--Volterra Interaction Matrices by Species Grouping: Optimal Groupings Are Unpredictable}
\author{
	Christopher R. P. Brown
}
\date{}

@@

The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
The total Akaike weight assigned to models in which the rows and columns used the same grouping was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).

>>>>

%Referencing
\import{reference-styles/}{ecology.tex}
\addbibresource{bibliography/references.bib}
\addbibresource{references.bib}
\usepackage{placeins} %Provides \FloatBarrier

@@

%Title Page
\title{Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable}
\author{
	Christopher R. P. Brown
}
\date{}

@@

The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.

Considering only models in which the rows and columns used the same grouping, the AIC values ranged from \aicnum{\Sexpr{min(brute_data$equivalently_grouped_statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$equivalently_grouped_statistics$aic)}}; neither the best nor worst overall models had equivalently grouped rows and columns.
The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
